Implementation of a Fuzzy Rule-Based Classifier using Genetic Algorithms

### 2017-12-13 Article/article.tex
Writing some stuff in FL section

\subsection{Bla}

@@

>>>>

Fuzzy Logic is a theory to deal with uncertainty.
Zadeh introduced fuzzy set theory in 1965. Usually logic is seen with a Boolean approach. Is a whale a fish? Yes or no, there is no in between. This is what we call a \textit{crisp set}. Either it belongs to the set, or it's a nonmember. 
However, fuzzy sets are made to encompass the sometimes uncertain nature of an assertion. An object will belong to a fuzzy set with a certain truth value which is called the \textit{grade of membership}.
Fuzzy Logic have been applied in a lot of domain, notably in control systems and in artificial intelligence.

Fuzzy set is defined by Membership function

Fuzzy variable/Linguistic concepts

A fuzzy system goes through three processes : fuzzification, inference, and finally defuzzification. Each of these process will be described.

@@

Fuzzification is the first step of a fuzzy system. It takes crisp input values and turn them into fuzzy values through our membership functions.
For our classifier. We have designed 3 linguistics variables for each of the parameters, that is in total 12 membership functions.
The three linguistics variables are SMALL, MEDIUM and LARGE. We decided that they would be the same functions for each of the parameters.

(PLOT OF THE THREE FUNCTIONS??)
